%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Mohammad Tofik} \\ \vspace{1pt}
    Basti, Uttar Pradesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 9113585712 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{itsmemdtofik@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/itsmemdtofik/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/itsmemdtofik}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal Institute Of Technology, MAHE}{Aug 2020 -- Nov 2023}
      {B.Tech in Computer Science and Engineering $|$ \textbf{CGPA - 8.0}}{Manipal, Karnataka}
      \resumeSubheading
      {Dr. T M A Pai Polytechnic}{June 2017 -- Aug 2020}
      {Diploma in Computer Science and Engineering $|$ \textbf{CGPA - 8.0}}{Manipal, Karnataka}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{COURSEWORK AND SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Web Development
                \item Database Management
                \item Operating System
                \item Computer Networks
                \item Cloud Computing
                \item Linux
                
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Western Digital (SanDisk)}{Jan 2023 -- Jun 2023}
      {Software Developer Intern}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Interned on a project involving data encryption for secure search capabilities across cloud storage and databases, ensuring privacy and accessibility.}
        \resumeItem{Protecting data through encryption while maintaining searchable capabilities.}
        \resumeItem{SSE utilizes a confidential symmetric key for encryption, ensuring authorized access.}
        \resumeItem{Facilitates secure search functionality on encrypted data in various applications like cloud storage and databases, preserving data privacy and accessibility.}
      \resumeItemListEnd

    \resumeSubheading
      {Thaniya Technologies}{May 2022 -- July 2022}
      {Full Stack Developer Intern}{Mengalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Assisted in development of the front end of a web application for Browser and Android using Django Framework.}
        \resumeItem{Worked with MySQL to manage user inputted data across multiple platforms for web.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Utilized VSCode Editor as a development environment in order to visualize the web application for the browser and Android.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
  {\textbf{FIDO2 Authentication System} $|$ \emph{Java, FIDO2, WebAuthn, CTAP, HOTP, TOTP} $|$
  \href{https://github.com/itsmemdtofik/RSA-Authentication-System} {\textbf{GitHub}}}{Apr 2024}
  \resumeItemListStart
    \resumeItem{Developed a secure authentication system leveraging FIDO2 standards for two-factor authentication.}
    \resumeItem{Implemented cryptographic key operations for passkey technology.}
    \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
  \resumeItemListEnd

          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{SSE Engine} $|$ \emph{Core Java, Apache Tika, SSE, SHA-256, PKDF2, HMAC} $|$
          \href{https://github.com/itsmemdtofik/SSE-Engine} {\textbf{GitHub}}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{Implemented the SSE(Symmetric Searchable Encryption) technique to provide  highly efficient privacy preserving Encrypted Index based File Search.}
            \resumeItem{Implemented UI to select the multiple file from the file system to create a reverse index for efficiently search over encrypted data.}
            \resumeItem{Our implementation involves, Document Pre-processing, Key Management (Key Generation), Encryption, Hashing, Compressed Map, Searching and Decryption.}
            \resumeItem{The server receives the search token and uses it to search through the encrypted dataset, returning encrypted results. The server learns nothing about the query or the actual data.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Ecommerce Website} $|$ \emph{Django,Python, HTML, CSS, Bootstrap, JavaScript, SQLite3} $|$
          \href{https://github.com/itsmemdtofik/eCommerce} {\textbf{GitHub}}}{May 2022}
          \resumeItemListStart
            \resumeItem{Created a responsive eCommerce platform that allows users to browse products, register, login, and add items to the shopping cart.}
            \resumeItem{Processed user inputted information in the back-end of the app to return a subtotal price based on the product selected.}
            \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio} \\
     \textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, JUnit, WordPress} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
